### 2014-01-31 patchy-selection-paper.tex
additional citation
.

\paragraph{Previous work} 
We will make use of several previous results from the literature. 
\citet{haldane1948theory}, working with the one dimensional partial differential equation,
showed that with large patches, the spatial scale over which the two types intergrade is given by $\sigma/\sqrt{s}$,
with $s$ either $s_m$ or $s_p$ as appropriate.
\citet{slatkin1973geneflow}, in the same setting,
showed that if the physical width of the patch is less than $2 \tan^{-1} (\sqrt{s_m/s_p})$, 
then there is no stable equilibrium with both $b$ and $B$ present,
so that migrational swamping prevents $B$ from establishing \citep[see also][ for a review]{lenormand2002limits}.
\citet{barton1987establishment}, using general theory of \citet{pollak1966survival}, showed (again in one dimension) 
that this critical patch size also holds in a stochastic framework.
\citet{barton1987establishment} also showed that
for patches above this critical size,
the probability of establishment of a new mutant that appears at distance $r$ from the patch
decays exponentially with distance from the patch, with the scale given by $\sigma/\sqrt{s_m}$,
and that mutations appearing within the patch have probability of establishment
less than the probability for a panimictic population,
but approaching this as the size of the patch increases.
(This latter panmictic probability of establishment we denote $p_e$,
and often approximate by $2 s_p / \xi^2$ \citep{haldane,fisher}.)
This result holds quite generally for a geographically spread population that experiences a uniform selection
pressure \citep{maruyama1970fixation,cherry2003diffusion}.

>>>>

\paragraph{Previous work} 
We will make use of several previous results from the literature. 
XXX cite nagylaki 1974: does 2d clines XXX
\citet{haldane1948theory}, working with the one dimensional partial differential equation,
showed that with large patches, the spatial scale over which the two types intergrade is given by $\sigma/\sqrt{s}$,
with $s$ either $s_m$ or $s_p$ as appropriate.
\citet{slatkin1973geneflow}, in the same setting,
showed that if the physical width of the patch is less than $2 (\sigma/\sqrt{s_p}) \tan^{-1} (\sqrt{s_m/s_p})$, 
then there is no stable equilibrium with both $b$ and $B$ present,
so that migrational swamping prevents $B$ from establishing \citep[see also][ for a review]{lenormand2002limits}.
\citet{barton1987establishment}, using general theory of \citet{pollak1966survival}, showed (again in one dimension) 
that this critical patch size also holds in a stochastic framework.
\citet{barton1987establishment} also showed that
for patches above this critical size,
the probability of establishment of a new mutant that appears at distance $r$ from the patch
decays exponentially with distance from the patch, with the scale given by $\sigma/\sqrt{s_m}$,
and that mutations appearing within the patch have probability of establishment
less than the probability for a panimictic population,
but approaching this as the size of the patch increases.
(This latter panmictic probability of establishment we denote $p_e$,
and often approximate by $2 s_p / \xi^2$ \citep{haldane,fisher}.)
This result holds quite generally for a geographically spread population that experiences a uniform selection
pressure \citep{maruyama1970fixation,cherry2003diffusion}.
